Information Disclosure in Dynamic Innovation Contests

### 2025-05-14 paper/Paper.tex
update-data-clean

\subsection{Literature Review}

@@

\section{Estimation}

@@

\subsection{Data Generating Process}

@@

\subsection{Bayesian Framework}

@@

\section{Synthetic Data}

@@

\subsection{Asymptotic Convergence}

@@

\subsubsection{Replicated Experiments.}

@@

\subsubsection{Long Term Contest.}

@@

\subsubsection{Multiple Players.}

@@

\section{Case Study}\label{sec-kaggle-application}

@@

@@

regression: $\lambda$ and the proportion of data release

>>>>

\subsection{Related Literature}

@@

\section{Estimation Framework}

@@

\subsection{Data-Generating Process}

@@

\subsection{Bayesian Estimation Framework}

@@

\section{Synthetic Experiments}

@@

\subsection{Asymptotic Properties}

@@

\subsubsection{Replications.}

@@

\subsubsection{Long-Horizon Contest.}

@@

\subsection{Staggered Entry of Multiple Players}

@@

\section{Empirical Application}\label{sec-kaggle-application}

@@

\subsection{Mapping the Model to the Data}

@@

1. How to select key players? Top $n$ in final private leaderboard

2. How to deal with monetary prize and other forms (knowledge, reputation)? The baseline reward is ``knowledge + reputation"; Later, we can verify the effect of monetary rewards (additional prize).

3.

\subsection{Structural Validation}

relation between $\lambda$ and the proportion of data release?
